\bf Title here

### 2019-11-20 fertile.tex
merge

\bigskip
\begin{abstract}
The text of your abstract. 200 or fewer words.
\end{abstract}

>>>>

\bigskip
\begin{abstract}
The production of reproducible research is key for advancing our
scientific knowlege, encouraging transparency, collaboration, and
understanding. However, there is no clear consensus on the standards
that constitute research reproducibility. In an attempt to build a
reproducibility framework in the R community, several packages have been
developed to address different aspects of reproducibility, but none are
comprehensive. In this paper, we present \texttt{fertile}, an R package
with an extensive selection of functions designed to thoroughly test
reproducibility. Fertile makes creating a reproducibile project as easy
as possible for users of all levels of sophistication, providing a
simple and comprehensive framework for testing reproducibility in the R
community.

Note: should we add something about the idea of testing the package in a
classroom?
\end{abstract}
